Matching Bullets

### 2015-11-30 imaging-paper.Rnw
crosscut sections for bullet 1 barrel 3.

\paragraph{Varying crosscuts}
The crosscut at which a comparison is done matters -- as crosscuts are further apart, more pronounced differences between the crosscuts show up. For bullet land 1-5 from barrel 1 crosscuts at intervals of 50$\mu m$ between 150$\mu m$  and 450$\mu m$  are compared to a crosscut at 100$\mu m$. The initially almost perfect match (consolidated by a CMS of nineteen) between the  crosscuts deteriorates with increasing distance to a very questionable match at $x = 350\mu m$ and non-matches further apart. Only if the crosscut is within 200$\mu m$ do we get a good visual match. Given that alignment in the microscope is not perfect, we should take this into account in the automatic matching routine by evaluating matches at several cross sections.
\begin{figure}
<<crosscuts-vary, echo=FALSE, fig.width = 14, fig.height = 21, out.width = '\\linewidth', cache=TRUE, warning = FALSE>>=
paths <- file.path(datadir, dir(datadir))
crosscuts <- seq(100, 450, by = 50)
lof <- processBullets(paths[5], x = crosscuts)
lof$bullet <- paste(lof$bullet, lof$x)

@@

grid.arrange(lop[[1]], lop[[2]], lop[[3]], lop[[4]], lop[[5]], lop[[6]], 
             lop[[7]],
             ncol = 1)
@
\caption{\label{fig:crosscuts}Overview of the variations in the surface along different crosscuts. Crosscut at $x = 100$ is compared to crosscuts every 50$\mu m$. With every step away from the original crosscut site, the number of differences between the crosscuts increases, and the number of maximum CMS decreases from initially 19 to only 3 at $x = 400$ and $x = 450$. }
\end{figure}

>>>>

\paragraph{Varying crosscuts}
The crosscut at which a comparison is done matters -- as crosscuts are further apart, more pronounced differences between the crosscuts show up. For bullet land 1-5 from barrel 1 crosscuts at intervals of 50$\mu m$ between 150$\mu m$  and 450$\mu m$  are compared to a crosscut at 100$\mu m$. The initially almost perfect match (consolidated by a CMS of nineteen) between the  crosscuts deteriorates with increasing distance to a very questionable match at $x = 350\mu m$ and non-matches further apart. Only if the crosscut is within 200$\mu m$ do we get a good visual match. Given that alignment in the microscope is not perfect, we should take this into account in the automatic matching routine by evaluating matches at several cross sections. \hh{XXX We're not doing that yet, but it might help - particular for bullets that have larger break-offs at the bottom.}
\begin{figure}
<<crosscuts-vary, echo=FALSE, fig.width = 14, fig.height = 21, out.width = '\\linewidth', cache=TRUE, warning = FALSE>>=
paths <- file.path(datadir, dir(datadir))
crosscuts <- seq(100, 450, by = 50)
lof <- processBullets(paths[5], x = crosscuts)
lof$bullet <- paste(lof$bullet, lof$x)

@@

grid.arrange(lop[[1]], lop[[2]], lop[[3]], lop[[4]], lop[[5]], lop[[6]], 
             lop[[7]],
             ncol = 1)
@
\caption{\label{fig:crosscuts}Overview of the variations in the surface along different crosscuts. Crosscut at $x = 100$ is compared to crosscuts every 50$\mu m$. With every step away from the original crosscut site, the number of differences between the crosscuts increases, and the number of maximum CMS decreases from initially 19 to only 3 at $x = 400\mu m$ and $x = 450\mu m$. }
\end{figure}

\hh{XXX Does this give us a way to automatically check for the bottom of the bullet? -- We could try to take two cross sections - maybe 50 or 100 $\mu m$ apart. If they don't match, we need to go a bit higher with the lower cross cut. Attempt at this is shown in Figure~\ref{fig:crosscuts2}.}

\begin{figure}
<<crosscuts-vary-b31, echo=FALSE, fig.width = 7, fig.height = 10, out.width = '\\linewidth', cache=TRUE, warning = FALSE>>=
paths <- file.path(datadir, dir(datadir))
crosscuts <- seq(100,225, by=25)
lof <- processBullets(paths[37], x = crosscuts)
lof$bullet <- paste(lof$bullet, lof$x)

reslist <- lapply(1:length(crosscuts[-1]), function(i) {
  b2 <- subset(lof, x %in% crosscuts[i:(i+1)])
  lofX <- bulletSmooth(b2)
  lofX <- bulletAlign(lofX)  
  threshold <- bulletPickThreshold(lofX, thresholds = seq(0.3, 1.5, by = 0.05))

grid.arrange(lop[[1]], lop[[2]], lop[[3]], 
             lop[[4]], lop[[5]], 
             ncol=1)
@
\caption{\label{fig:crosscuts2}Varying crosscuts for barrel 3, bullet 1. Initially, the match between crosscuts 25$\mu m$ apart is affected strongly by break off at the bottom of the bullet. At a crosscut level of $175\mu m$ the bullet pattern stabilizes. For this land, matches should not be attempted to lower crosscuts.}
\end{figure}
